{\huge \textbf{Unshuffling Permutations}}

### 2016-04-09 slides/slides.tex
Ameliorations slides

\uncover<4->{%
\begin{block}{Open problem}
    Enumeration of square (binary) words.
\end{block}}
\end{frame}

@@

        \uncover<4->{%
        \item To prove that $\mu_{\sigma, \pi}$ is a square, we show
        that $\mu_{\sigma, \pi}$ admits a perfect matching satisfying
        $\mathbf{P_1}$ and~$\mathbf{P_2}$.}
    \end{itemize}
  \end{block}}
\end{frame}

>>>>

\uncover<4->{%
\begin{block}{Open problem \BIB{Henshall, Rampersad, Shallit}{2012}}
    Enumeration of square (binary) words.
\end{block}}
\end{frame}

@@

        \uncover<4->{%
        \item We use the fact that $\mu_{\sigma, \pi}$ is a square iff
        $\mu_{\sigma, \pi}$ admits a perfect matching satisfying
        $\mathbf{P_1}$ and~$\mathbf{P_2}$.}
    \end{itemize}
  \end{block}}
\end{frame}
